---
title: "Exercise 2"
output: html_document
code_folding: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, comment = "")
```


1. Open an RStudio session
<small>https://github.com/ifetzer/RStudioForTeaching</small>
2. Load the `gapminder` data

```{r}
dat <- gapminder::gapminder
```

3. `country` is of the class `factor`, discuss in couples what are they and when are useful?
    - Tip: `help(factor)` & `help(levels)`

```{r}
# write your answer here
```


4. How many countries has the `gapminder` data?
```{r}
# write your answer here
```

5. Write a function to calculate the average
    - Test it in small cases
```{r}
# write your answer here
```


6. For every country in the dataset calculate the average life expectancy, the range of the popluation, and the median GDP per capita
    - Tip: `for()`, `median()`, `range()`
  
```{r}
# write your answer here
```

7. Use the result to plot:
    - Average `lifeExp` vs median `gdpPercap`

```{r}
# write your answer here
```

8. For every year in the dataset calculate the average life expectancy across all countries. Plot the result over time
    - `??base::plot`

```{r}
# write your answer here
```
